Some Nice Title Goes Here, Eventually\ldots

### 2014-08-31 doc/tacs2014/article.tex
More or less done with I-III, IVab

	Given that the category search space for Japanese characters is an order of magnitude larger and contains a vastly differing set of
	characteristics than its western counterparts, the same designs that yield highly accurate results on 
	western handwriting recognition tasks will not perform satisfactory when applied to asian script \cite{jager2003state, tappert1990state, liu2004online}
	-- unless the solution relies on complex and computationally expensive techniques, such as  ``deep'' neural networks. \cite{ciresan2012multi}

	In continuation, we describe a flexble, modular design scheme that splits the identification task into coarse and fine steps,
	thereby reducing the complexity of each undertaking. The design scheme also permits replacing the segmentation and classification strategies,
	and facilitates the parallelization of the fine classification components.

	\begin{figure}
		\centering
		\begin{tikzpicture}[font=\small]
			\begin{axis}[
				ycomb,
				xlabel={Number of strokes},
				ylabel={Number of characters},
			]
				%\addplot[fill=white] coordinates {
				\addplot [] coordinates {
					(1, 6)
					(2, 32)
					(3, 64)
					(4, 115)
					(5, 151)
					(6, 199)
					(7, 318)
					(8, 434)
					(9, 473)
					(10, 544)
					(11, 581)
					(12, 581)
					(13, 532)
					(14, 435)
					(15, 434)
					(16, 369)
					(17, 299)
					(18, 207)
					(19, 175)
					(20, 135)
					(21, 106)
					(22, 69)
					(23, 49)
					(24, 37)
					(25, 20)
					(26, 12)
					(27, 8)
					(28, 6)
					(29, 3)
					(30, 2)
				};
			\end{axis}
		\end{tikzpicture}
		\caption{Distribution of 6,400 kanji by number of stroke. Min = 2, Max = 581. \emph{Data source: KanjiVG.} \cite{kanjivg}}
		\label{fig_kanji_stroke_hist}
	\end{figure}

@@

	% Took A-H classification from here
	In \cite{nakai2001substroke}, the authors adapt a continuous speech recognition algorithm utilizing
	hidden Markov models for the purpose of online kanji recognition. Captured strokes are segmented into
	substrokes and classified according to directionality (see figure \ref{fig_stroke_categories}),
	and these characteristics are in turn employed as dictionary search keys.

	After structuring the search space by clustering, Yang et. al. perform two--stepped offline recognition by first
	comparing the input character to the centroids of each cluster, and then distinguishing between the members of the cluster
	whose centroid most closely matched the input. \cite{yang2003accelerating},

	In \emph{Hybrid pen-input character recognition system based on integration of online-offline recognition},
	the authors integrate online and offline recognition strategies, leveraging the advantages of each technique.
	In addition to a discussion of various integration techniques, two feature extraction methods are described: 
	a gradient--based technique for offline input, and a recursive substroke extractor for online input.

	``Online Handwritten Kanji Recognition Based on Inter-stroke Grammar'' uses the A-H0-9 classification scheme,
	and discusses the hierarchical structure of kanji.

	Should we mention alternative solutions, such as SVMs? Zinnia (w/ Tomoe) does quite a good job, for instance. Not sure if there
	are academic evaluations/references, though.

@@

@@

	\begin{figure}
		\centering
		\includegraphics[width=2.75in]{./fig/model-overview.eps}
		\caption{The model consists of four components: a feature extractor, a clustering strategy,
			a router (coarse classifier), and a fine--grained classifier.}
		\label{fig_model_overview}
	\end{figure}

	The input data is processed by an algorithm, generating a coarse, n--dimensional representation of its principal features.
	The feature vector is used to select which cluster the input belongs to.

	A higher feature vector dimensionality allows for the construction of more finely--tuned clusters, but may well increase
	the likelihood of ``misrouting,'' resulting in a failed classification.
	% Actually, if a character is not found within the specified CANN, it could be passed to a neighboring cluster of similar composition

	The coarse classifier may work on either online or offline input, or potentially a union of them both.
	Examples of feature extractors include the LTM algorithm, and gradient--based solutions, both outlined in \cite{tanaka1999hybrid}.

>>>>

	Although the characters are vast in number and differ significantly from one another in terms of complexity (see figures \ref{fig_kanji_sample}
	and \ref{fig_kanji_stroke_hist}), the writing system itself is not arbitrary. Any kanji may be broken down into smaller units, known as graphemes, 
	and they are commonly ``classified'' by basic, frequently--ocurring components referred to as radicals.
	Furthermore, stroke order is dictated by a set of rules. In essence, kanji are written from top to bottom and left to right within imagined squares. \cite{foerster1994kanji}

	These properties are often leveraged in kanji recognition systems, but not without penalty: relying on the correct stroke order during online
	recognition, for instance, severely impacts recognition rates when a user provides ``erroneous'' input -- even though it might still be \emph{visually} correct. \cite{shin2002optimal}

	While certain aspects such as noise reduction and normalization remain similar across systems, the characteristics mentioned above result in
	recognition systems designed for western input not performing satisfactorily when applied to asian script \cite{jager2003state, tappert1990state, liu2004online}
	-- unless the solution relies on complex techniques such as  ``deep'' neural networks. \cite{ciresan2012multi}

	%Given that the category search space for Japanese characters is an order of magnitude larger and contains a vastly differing set of
	%characteristics than its western counterparts, the same designs that yield highly accurate results on 
	%western handwriting recognition tasks do not perform satisfactorily when applied to asian script \cite{jager2003state, tappert1990state, liu2004online}
	%-- unless the solution relies on complex and computationally expensive techniques, such as  ``deep'' neural networks. \cite{ciresan2012multi}

	\begin{figure}
		\centering
		\begin{tikzpicture}[font=\small]
			\begin{axis}[
				ycomb,
				xlabel={Number of strokes},
				ylabel={Number of characters},
			]
				%\addplot[fill=white] coordinates {
				\addplot [] coordinates {
					(1, 6)
					(2, 32)
					(3, 64)
					(4, 115)
					(5, 151)
					(6, 199)
					(7, 318)
					(8, 434)
					(9, 473)
					(10, 544)
					(11, 581)
					(12, 581)
					(13, 532)
					(14, 435)
					(15, 434)
					(16, 369)
					(17, 299)
					(18, 207)
					(19, 175)
					(20, 135)
					(21, 106)
					(22, 69)
					(23, 49)
					(24, 37)
					(25, 20)
					(26, 12)
					(27, 8)
					(28, 6)
					(29, 3)
					(30, 2)
				};
			\end{axis}
		\end{tikzpicture}
		\caption{Distribution of 6,400 kanji by stroke count. Min = 2, Max = 581. \emph{Data source: KanjiVG.} \cite{kanjivg}}
		\label{fig_kanji_stroke_hist}
	\end{figure}

@@

	After structuring the search space by clustering, Yang et. al. perform two--stepped offline recognition by first
	comparing the input character to the centroids of each cluster, and then distinguishing between the members of the cluster
	whose centroid most closely matched the input. \cite{yang2003accelerating}

	In \emph{Hybrid Pen--Input Character Recognition System Based on Integration of Online--Offline Recognition},
	the authors present a system that leverages the advantages provided by each type of recognition.
	In addition to a discussion of various integration techniques, two feature extraction methods are described in detail: 
	a gradient--based technique for offline input, and a recursive substroke extractor for online input.

	% Got A-H classification from here
	In \cite{nakai2001substroke}, the authors adapt a continuous speech recognition algorithm utilizing
	hidden Markov models for the purpose of online kanji recognition. Captured strokes are segmented into
	substrokes and classified based on directionality (see figure \ref{fig_stroke_categories});
	the result is thereafter employed as dictionary search keys.

	\emph{Online Handwritten Kanji Recognition Based on Inter--Stroke Grammar} explains the hierarchical structure of kanji,
	and explores how to leverage this information using stochastic context--free grammars. \cite{ota2007online}

	Finally, albeit not directly applied to Japanese handwriting recognition, \emph{Best Practices for Convolutional Neural Networks
	Applied to Visual Document Analysis} by Simard, et. al. underlines the potential of convolutional neural networks 
	and provides a variety of techniques and guidelines directly applicable to the development of a fine--grain classifier. \cite{simard2003best}

@@

	Taking into consideration the issues presented in section \ref{sec:problem_description}
	%the problem posed by the large number of candidates, the characteristics of the kanji writing system,
	and the many influential works reviewed in section \ref{sec:previous_work}, we attempt to define a general description of a flexble, modular 
	design scheme that splits the identification task into coarse and fine phases -- thereby reducing the complexity of each undertaking -- and 
	additionally permits replacing the normalization, segmentation, and classification strategies.%, and facilitates the parallelization of fine classification.
	The design is applicable to online as well as offline recognition tasks.

	\begin{figure}[b]
		\centering
		\includegraphics[width=2.75in]{./fig/model-overview.eps}
		\caption{The model consists of five components: input normalization methods, a feature extractor,
			a clustering strategy, a router (coarse classifier), and a fine--grained classifier.}
		\label{fig_model_overview}
	\end{figure}

	\subsection{Input normalization}

	Improving the input data, especially by making it more uniform with respect to available training data, has the potential
	to greatly increase recognition rates. In the case of offline input, techniques include noise--reduction,
	cropping, and scaling; for online input, strokes could be analyzed and altered on--the--fly to increase consistency.
	Other possibilities include blurring or otherwise distorting input data in order to generalize it. \cite{razzak2009combining}

	The feature extraction algoritm should take either online, offline, or combined input and rapidly generate
	an n--dimensional vector representation of the provided data. The output should be sufficient for the
	routing component to reliably distinguish within which candidate subset the fine classifier should search.

	Generally speaking, a higher feature vector dimensionality would allow for the construction of more finely--tuned clusters,
	but this might well increase the likelihood of misrouting.%, resulting in a failed classification.
	% Actually, if a character is not found within the specified CANN, it could be passed to a neighboring cluster of similar composition

	Examples of feature extractors include recursive substroke segmentation and image gradation, both outlined in \cite{tanaka1999hybrid}.

@@
